\begin{thebibliography}{unsrt}

\bibitem{1}
    E. L. Lawler. \emph{A note on the complexity of the chromatic number problem.} Information Processing Letters. Volume 5, number 3: 66--67, August 1976. \url{https://inria.hal.science/hal-04716389v1/document}

\bibitem{2}
    I. Schiermeyer. \emph{Deciding 3-colourability in less than $\mathcal{O}(1.415^n)$ steps.} International Workshop on Graph-Theoretic Concepts in Computer Science, 1993.

\bibitem{3}
    R. Beigel and D. Eppstein. \emph{3-coloring in time $\mathcal{O}(1.3289^n)$}. Journal of Algorithms. Volume 54, issue 2: 168--204, February 2005. \url{https://arxiv.org/abs/cs/0006046}

\bibitem{4}
    L. Meijer. \emph{3-Coloring in Time $\mathcal{O}(1.3217^n)$}. ArXiv. abs/2302.13644, February 2023. \url{https://arxiv.org/abs/2302.13644}

\bibitem{5}
    A. Blum and D. Karger. \emph{An $\mathcal{\widetilde{O}}(n^{3/14})$-coloring algorithm for 3-colorable graphs.} August, 1996. \url{http://www.hirata.nuee.nagoya-u.ac.jp/~sharryx/BKMS3-14.pdf}

\bibitem{6}
    J. Moon and L. Moser. \emph{On cliques in graphs.} Israel Journal of Mathematics. Volume 3: 23–-28, March 1965. \url{https://users.monash.edu.au/~davidwo/MoonMoser65.pdf}

\bibitem{7}
    D. R. Wood. \emph{On the number of maximal independent sets in a graph.} ArXiv. 1104.1243, April 2011. \url{https://arxiv.org/abs/1104.1243}

\bibitem{8}
    D. S. Johnson and M. Yannakakis and C. H. Papadimitriou. \emph{On generating all maximal independent sets}. Information Processing Letters. Volume 27, number 3: 119--123, March 1988. \url{https://www.cs.huji.ac.il/course/2005/mssys/independent.pdf}


\end{thebibliography}
